---
title: "readmissionratebpjsk"
author: "aldilas"
date: "4/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load library
```{r message=FALSE, warning=FALSE, MESSAGE=FALSE}
library(haven)
library(tidyverse)
library(psych)
library(lubridate)
library(survey)
library(eeptools)
library(stringr)
library(party)
library(sjmisc)
library(data.table)
library(readxl)
```

## Load data FKRTL & Kepesertaan

```{r}
kepesertaan <- read_dta("C:/Users/aldilas/Documents/BPJSKv2/01 KEPESERTAAN 260819.dta") %>% select(PSTV01, PSTV03, PSTV05, PSTV07, PSTV08) %>% as_factor(levels = "both")
fkrtl <- read_dta("C:/Users/aldilas/Documents/BPJSKv2/04 FKRTL 260819.dta") %>% as_factor()
diagnosissekunder <- read_dta("C:/Users/aldilas/Documents/BPJSKv2/05 FKRTL Diagnosis Sekunder 260819.dta") %>% as_factor()
diagnosisprimer <- select(fkrtl, PSTV01, FKL02, FKL15, FKL16, FKL16A, FKL17, FKL18, FKL18A) %>% arrange(FKL02)
fkrtl$PSTV01 <- as.character(fkrtl$PSTV01)
kepesertaan$PSTV01 <- as.character(kepesertaan$PSTV01)
fkrtl$FKL02 <- as.character(fkrtl$FKL02)

```

## Join diagnosis
```{r}
kodediagnosis <- read_excel("BPJSKv2/Kode ICD10 untuk diagnosis FKRTL.xlsx", sheet = "Sheet1")
diagnosissekunder <- arrange(diagnosissekunder, FKL02)
diagnosisjoin1 <- left_join(diagnosisprimer, diagnosissekunder, by = "FKL02", copy = F, keep = F)
diagnosisjoin <- left_join(diagnosisjoin1, kodediagnosis, by = c("FKL15"))
kodediagnosis$FKL24_A <- kodediagnosis$FKL15
diagnosisjoin <- left_join(diagnosisjoin, kodediagnosis, by = "FKL24_A")
```


## Calculate LOS and remove inhospital stay less than 1 days
```{r}
fklranap1 <- fkrtl %>% arrange(PSTV01, FKL03) %>% filter(FKL10 == 2 & FKL14 != 2)
fklranap1$los <- as.Date(as.character(fklranap1$FKL04), format="%Y-%m-%d")-
  as.Date(as.character(fklranap1$FKL03), format="%Y-%m-%d")
fklranap2 <- fklranap1 %>% filter(los > 1 & !is.na(FKL50)) %>% mutate(year = lubridate::year(FKL03))
fklranap2$interval = NA
```

## Join with kepesertaan
```{r}
fklranap3 <- left_join(fklranap2, kepesertaan, by=c("PSTV01"))
fklranap3 <- fklranap3[!duplicated(fklranap3$FKL02), ]
fklranap <- fklranap3 %>% filter(FKL03 >= PSTV03)
```

## Calculate age & Discretize age groups
```{r}
age <- round(age_calc(na.omit(as.Date(fklranap$PSTV03, "%Y-%m-%d")),
                      enddate=as.Date(fklranap$FKL03, "%Y-%m-%d"),
                      units= "years"))

fklranap$age[!is.na(fklranap$PSTV03)] <- age
df <- fklranap %>% mutate(ageGroup = cut(age, breaks=c(0,5,12,17,26,36,46,56,66,120), labels=c("Balita", "Anak-anak", "Remaja awal", "Remaja akhir","Dewasa awal", "Dewasa akhir", "Lansia awal", "Lansia akhir", "Manula"), include.lowest = TRUE, right=FALSE))
```

## Split by year
```{r}
df_2015 <- df %>% filter(year == 2015)
df_2016 <- df %>% filter(year == 2016)
```

## Calculate interval between 2 visits
```{r}
df_2015 <- arrange(df_2015, PSTV01, FKL03)
for (i in 2:nrow(df_2015)){
  if(df_2015$PSTV01[i]==df_2015$PSTV01[i-1]){
    df_2015$interval[i] <- as.integer(difftime(df_2015$FKL03[i],df_2015$FKL04[i-1]))
  }
}

df_2016 <- arrange(df_2016, PSTV01, FKL03)
for (i in 2:nrow(df_2016)){
  if(df_2016$PSTV01[i]==df_2016$PSTV01[i-1]){
    df_2016$interval[i] <- as.integer(difftime(df_2016$FKL03[i],df_2016$FKL04[i-1]))
  }
}

df <- arrange(df, PSTV01, FKL03)
for (i in 2:nrow(df)){
  if(df$PSTV01[i]==df$PSTV01[i-1]){
    df$interval[i] <- as.integer(difftime(df$FKL03[i],df$FKL04[i-1]))
  }
}
```

## Labelize
```{r}
df <- df[!duplicated(df$FKL02), ]
df_2015 <- df_2015[!duplicated(df_2015$FKL02), ]
df_2016 <- df_2016[!duplicated(df_2016$FKL02), ]

df$readmission <- ifelse(is.na(df$interval), "I", ifelse(df$interval > 30 | grepl("Z", df$FKL15) | grepl("Z", df$FKL17), "OR", ifelse(df$interval <= 30 & df$interval >= 0, "UR", NA)))

df_2015$readmission <- ifelse(is.na(df_2015$interval), "I", ifelse(df_2015$interval > 30 | grepl("Z", df_2015$FKL15) | grepl("Z", df_2015$FKL17), "OR", ifelse(df_2015$interval <= 30 & df_2015$interval >= 0, "UR", NA)))

df_2016$readmission <- ifelse(is.na(df_2016$interval), "I", ifelse(df_2016$interval > 30 | grepl("Z", df_2016$FKL15) | grepl("Z", df_2016$FKL17), "OR", ifelse(df_2016$interval <= 30 & df_2016$interval >= 0, "UR", NA)))

df <- filter(df, !is.na(readmission))
df_2015 <- filter(df_2015, !is.na(readmission))
df_2016 <- filter(df_2016, !is.na(readmission))
```

```{r}
library(readxl)
icdgroup <- read_excel("C:/Users/aldilas/Google Drive/readmission rate BPJSK/icdgroup.xlsx")
```

```{r WARNING=FALSE}
df$alphabet <- str_sub(df$FKL50, 1, 2)
df <- left_join(df, icdgroup, by = "alphabet")
```

## Renames
```{r}
setnames(df, old = c("PSTV01", "PSTV03", "PSTV06", "PSTV05", "PSTV07", "PSTV08", "FKL02", "FKL03", "FKL04", "FKL05", "FKL06A", "FKL07", "FKL09", "FKL13", "FKL14", "FKL15", "FKL17", "FKL21", "FKL23", "FKL30", "FKL48", "FKL50", "PSTV15"), new = c("ID", "DOB", "marital", "gender", "kelaspeserta", "membership", "visitID", "inDate", "outDate", "provinsi", "distrik", "rsowner", "rstype", "kelasrawat", "statusPulang", "index_icd_1", "index_icd_2", "inacbg", "severity", "prosedur", "cost", "index_diagnosis", "weight"))

setnames(df_2015, old = c("PSTV01", "PSTV03", "PSTV06", "PSTV05", "PSTV07", "PSTV08", "FKL02", "FKL03", "FKL04", "FKL05", "FKL06A", "FKL07", "FKL09", "FKL13", "FKL14", "FKL15", "FKL17", "FKL21", "FKL23", "FKL30", "FKL48", "FKL50", "PSTV15"), new = c("ID", "DOB", "marital", "gender", "kelaspeserta", "membership", "visitID", "inDate", "outDate", "provinsi", "distrik", "rsowner", "rstype", "kelasrawat", "statusPulang", "index_icd_1", "index_icd_2", "inacbg", "severity", "prosedur", "cost", "index_diagnosis", "weight"))

setnames(df_2016, old = c("PSTV01", "PSTV03", "PSTV06", "PSTV05", "PSTV07", "PSTV08", "FKL02", "FKL03", "FKL04", "FKL05", "FKL06A", "FKL07", "FKL09", "FKL13", "FKL14", "FKL15", "FKL17", "FKL21", "FKL23", "FKL30", "FKL48", "FKL50", "PSTV15"), new = c("ID", "DOB", "marital", "gender", "kelaspeserta", "membership", "visitID", "inDate", "outDate", "provinsi", "distrik", "rsowner", "rstype", "kelasrawat", "statusPulang", "index_icd_1", "index_icd_2", "inacbg", "severity", "prosedur", "cost", "index_diagnosis", "weight"))
```

## Label surgical or medical
```{r}
df$surgical <- ifelse(str_sub(df$inacbg,3,3)==1, "1", "0")
df_2015$surgical <- ifelse(str_sub(df_2015$inacbg,3,3)==1, "1", "0")
df_2016$surgical <- ifelse(str_sub(df_2016$inacbg,3,3)==1, "1", "0")
```

## Make NA explicit
```{r}
df$rstype <- fct_explicit_na(df$rstype, na_level = "(Missing)")
```

## Get Index admissions
```{r}
df_predict <- df %>% group_by(ID) %>% mutate(target = lead(readmission, order_by = ID), re_cost = lead(cost, order_by = ID))
df_predict$diseaseclass <- str_sub(df_predict$index_diagnosis, 1, 3)
```

## Demographics

```{r fig.width=10}
df %>% group_by(readmission) %>% tally(wt = weight) %>% mutate(proportion = round((n / sum(n))*100, 2))
df %>% group_by(gender, readmission) %>% tally(wt = weight) %>% mutate(proportion = round((n / sum(n))*100, 2))
df %>% group_by(readmission) %>% summarise(meanage = weighted.mean(age, weight), n = n(), SD = sd(age)) %>% mutate(proportion = (n/sum(n))*100)
df %>% filter(!is.na(ageGroup)) %>% group_by(readmission, ageGroup) %>% tally() %>% mutate(proportion = round((n / sum(n))*100,2))
df %>% filter(!is.na(readmission)) %>% group_by(readmission, membership) %>% summarise(meancost = mean(cost), sd = sd(cost), n = n()) %>% mutate(proportion = round((n/sum(n))*100, 2))
df %>% filter(!is.na(readmission)) %>% group_by(rstype, readmission) %>% summarise(n = n()) %>% mutate(proportion = round((n/sum(n))*100,2))
df %>% filter(!is.na(readmission)) %>% group_by(rstype) %>% tally() %>% mutate(proportion = (n/sum(n))*100)
df %>% filter(!is.na(readmission)) %>% group_by(statusPulang, readmission) %>% tally() %>% mutate(proportion = round((n/sum(n))*100,2))
df %>% filter(!is.na(readmission)) %>% group_by(severity, readmission) %>% tally() %>% mutate(proportion = round((n/sum(n))*100, 2))
df %>% filter(!is.na(readmission)) %>% group_by(readmission) %>% summarise(meanlos = weighted.mean(los, weight), sd = sd(los))
df %>% filter(!is.na(readmission)) %>% group_by(kelasrawat, readmission) %>% tally() %>% mutate(proportion = round((n/sum(n))*100, 2))
df %>% filter(!is.na(readmission)) %>% group_by(readmission) %>% summarise(meanlos = round(mean(los),2), sd=round(sd(los),2), min(los), max(los))
df %>% filter(!is.na(readmission)) %>% group_by(surgical) %>% summarise(n = n()) %>% mutate(proportion = (n/sum(n))*100)
df %>% filter(!is.na(readmission) & age > 17 & surgical == 1) %>% group_by(statusPulang) %>% summarise(n = n()) %>% mutate(proportion = (n/sum(n))*100)
df %>% mutate(index = ifelse(membership %in% c("PBI APBN","PBI APBD"), "PBI", "Non-PBI")) %>% group_by(index) %>% summarise(n = n()) %>% mutate(proportion = (n/sum(n))*100)
df %>% filter(!is.na(readmission)) %>% group_by(rsowner, readmission) %>% summarise(n = n()) %>% mutate(proportion = (n/sum(n))*100)
```

## Visualization
```{r}
hist(df$age, xlim=c(0,110), xlab="age")
ggplot(df, aes(x = ageGroup)) + geom_bar()
ggplot(df, aes(x = membership)) + geom_bar()
```

## Average cost
```{r}
diseasegroupcost <- df_predict %>% filter(target == "UR") %>% group_by(group) %>% summarise(meancost = mean(cost), readmissioncost = mean(re_cost), n = n()) %>% mutate(proportion = (n/sum(n))*100)
df_predict %>% filter(target == "UR") %>% group_by(target) %>% summarise(meancost = mean(cost), readmissioncost = mean(re_cost), n = n()) %>% mutate(proportion = (n/sum(n))*100)
hospitalcost <- df %>% group_by(rstype, readmission) %>% summarise(meancost = mean(cost), n = n()) %>% mutate(proportion = (n/sum(n))*100)
```

## Reshape diseasegroupcost table
```{r}
avgdiseasecost <- reshape2::dcast(diseasegroupcost, group ~ readmission, value.var = "meancost")
```

## Demographic of df_predict
```{r}
df_predict %>% group_by(target, surgical) %>% tally(wt = weight) %>% mutate(proportion = (n/sum(n))*100)
diseasereadmissionrate <- df_predict %>% group_by(group, target) %>% summarise(n = n()) %>% mutate(proportion = (n/sum(n))*100)
diseasereadmissionrate <- reshape2::dcast(diseasereadmissionrate, group ~ target, value.var = c("proportion"))
diseasereadmissionrate <- diseasereadmissionrate[order(-diseasereadmissionrate$UR),]
```


## Reshape 

## Collect most prevalent primary and secondary diagnosis
```{r}
indexicd1 <- df %>% filter(readmission == "UR") %>% group_by(index_icd_1) %>% tally() %>% mutate(proportion = (n/sum(n))*100) %>% arrange(-n)
indexicd2 <- df %>% filter(readmission == "UR") %>% group_by(index_icd_2) %>% tally() %>% mutate(proportion = (n/sum(n))*100) %>% arrange(-n)
```

## Logistic regression
```{r}
df_binomial <- df %>% filter(!grepl("F", df$alphabet))
df_binomial <- df_binomial %>% to_dummy(readmission, suffix = "label") %>% bind_cols(df_binomial) %>% select(ID, los, gender, age, ageGroup, severity, readmission_UR)
df_binomial$severity <- as.factor(df_binomial$severity)
fit <- glm(readmission_UR~severity+gender+ageGroup+los, data = df_binomial, family = binomial())
summary(fit)
exp(cbind(coef(fit), confint(fit)))
```

## Visualization
```{r}
plot(df_binomial$los, df_binomial$group)
boxplot(df_binomial$los)
```


## Visualization Sankey
```{r}
sankey_df <- na.omit(df_work) %>% select(ID, group, severity, re_group, class) %>% group_by(group, severity, re_group, class) %>% summarise(values = n()) %>% arrange(-values)
sankey_df$severity <- sub("^", "Tingkat ", sankey_df$severity)
```

```{r fig.height=9, fig.width=20}
sankey_df %>% filter(values >= 150) %>% 
  ggplot(aes(y=values, axis1=group, axis2 = severity, axis3=class)) +
    geom_alluvium(aes(fill = group)) +
    geom_stratum() +
    geom_label(stat = "stratum", label.strata = T) +
    scale_x_discrete(limits = c("group", "severity", "class")) +
    theme(legend.position = "bottom")
```

## Export csv
```{r}
write.csv(df, "bpjsreadmission.csv", row.names = F)
```

## Python interface
```{r}
library(reticulate)
use_python("C:/Users/aldilas/Miniconda3")
```

```{python}
from keras.models import Sequential

```